\section*{\Huge Abstract}

% Super-resolution (SR) is a fundamental problem in computer vision that aims to reconstruct high-resolution images from their low-resolution counterparts. Recent advances in deep learning have significantly improved SR performance; however, training high-performance neural networks for vision tasks often demands substantial computational resources, primarily due to the quadratic complexity of self-attention and the power requirements of modern GPUs. While inductive biases such as convolutional layers help reduce data requirements, they limit model flexibility. In this work, we introduce WaveMix, a novel deep learning architecture that leverages multi-level 2D Discrete Wavelet Transform (DWT) for efficient spatial token mixing without image unrolling or self-attention mechanisms. By exploiting key image priors—scale-invariance, shift-invariance, and edge sparsity—WaveMix reorganizes spatial information through a lossless and parameter-free transformation. This design not only expands the receptive field more rapidly than traditional convolutions but also significantly reduces computational overhead, enabling effective super-resolution with greater efficiency.
% \\
In recent years, accurate crowd counting in surveillance scenarios has gained significant attention due to its applications in public safety and urban planning. This report introduces a multi-stage, distributed intelligent video analytics pipeline that combines Frequency Exploitation Super-Resolution (FESR) and crowd counting, optimized for deployment on the NVIDIA DeepStream platform. The pipeline begins on a Windows host machine, where raw images are enhanced using WaveMix-SR, a state-of-the-art wavelet-based super-resolution model. The enhanced frames are compiled into a video stream and transmitted via RTSP to an NVIDIA Jetson device. On the Jetson, a GStreamer-based pipeline built with DeepStream SDK performs hardware-accelerated decoding and inference using FFNet, a lightweight and efficient crowd counting model. The system achieves real-time performance at 25 FPS, providing overlaid people count visualizations on a connected monitor.\\
Experiments conducted on the ShanghaiTech Part B dataset demonstrate that applying WaveMix-SR prior to FFNet inference significantly improves counting accuracy, especially in densely populated scenes. Quantitatively, our method achieves an MAE of 39.6, RMSE of 60.6, and maintains a throughput of 25 FPS on the Jetson device. These results validate the effectiveness of integrating frequency-domain super-resolution with edge-optimized inference for real-time crowd analytics.