\section{Deep Stream System}
\subsection{Motivation}
The proliferation of cameras and the increasing demand for automated visual understanding have created a pressing need for robust systems capable of solving complex computer vision problems in real time. Many modern applications, from smart city surveillance and retail analytics to industrial automation and autonomous systems, rely on accurately interpreting live video feeds to make timely decisions or extract valuable insights. However, these applications often involve processing multiple high-resolution video streams and executing computationally intensive deep learning models for tasks like object detection, image enhancement (such as Super Resolution), and specialized analytics like people counting. Traditional CPU-based approaches quickly become bottlenecks and are unable to deliver the necessary low-latency performance and high throughput.
\subsection{Goals}
This critical gap between the demand for real-time visual intelligence and the limitations of conventional processing power motivates the adoption of specialized frameworks like the NVIDIA DeepStream SDK. DeepStream is designed to bridge this gap by providing a GPU-accelerated, GStreamer-based platform that enables the efficient deployment of multi-stage AI pipelines, allowing developers to build sophisticated, real-time computer vision solutions that can effectively leverage the parallel processing capabilities of NVIDIA GPUs.
The primary goal is to develop and deploy an efficient, real-time people counting system by constructing a multi-stage AI pipeline. This pipeline specifically aims to:
\begin{itemize}
    \item To construct an optimized GStreamer pipeline within DeepStream for robust video ingestion, hardware-accelerated decoding, and efficient pre-processing, ensuring video data is primed for AI inference with minimal latency.
    \item To integrate and accelerate the custom people counting model using NVIDIA TensorRT via DeepStream's nvinfer element, and to accurately extract the numerical people count from the model's raw tensor output using buffer probes and metadata parsing.
    \item To enable real-time visualization of the analytical results by overlaying the people count directly onto the output video stream using nvdsosd, and to quantify the system's end-to-end performance by measuring its processing throughput in Frames Per Second (FPS) on an NVIDIA Jetson platform.
\end{itemize}
