\section{Overview}

In recent years, the field of manufacturing has witnessed significant advancements, particularly with the rise of additive manufacturing techniques such as 3D printing. This technology has revolutionized the way products are designed and produced, enabling rapid prototyping, customization, and the creation of complex geometries that were previously unattainable with traditional manufacturing methods \cite{3dprinting_review}.

However, despite its advantages, 3D printing is not without its limitations. It can be slower than traditional manufacturing for large-scale production, and some materials used in 3D printing may not offer the same strength or durability as those produced through conventional techniques \cite{3dprinting_pros_cons}.

Products that combine embedded electronics with 3D-printed housings do exist commercially. The BYTE-90 \cite{byte90_alxv}, for example, is a compact ESP32-based desk device enclosed in a PLA-printed shell. However, such products are typically passive in nature: they display a fixed set of pre-loaded animations and offer no direct means for the user to interact with the device. Their functionality is therefore narrow and fixed after purchase. Furthermore, they are priced at approximately \$100, placing them out of reach for many students and developers.

This project focuses on the integrated design of an ESP32 TTGO T-Display device with a custom 3D-printed housing. The ESP32 TTGO T-Display is a versatile microcontroller board that features built-in Wi-Fi and Bluetooth capabilities, making it ideal for a wide range of applications. Rather than targeting passive display-only output, this project produces a device with physical control buttons and a range of interactive applications, including games and utility programs, at a bill-of-materials cost of less than one-quarter of comparable commercial products. The housing is designed with Design for Manufacture and Assembly (DFMA) principles to ensure ease of fabrication, assembly, and maintenance.

The project covers the entire design process, from conceptualization and CAD modeling to FDM printing, electrical integration, firmware development, and testing. Through this project, we aim to demonstrate how embedded hardware, additive manufacturing, and software can be combined into a cohesive, user-centred product at minimal cost.