\section{Super Resolution}
\subsection{Motivation}
Deep learning models have achieved remarkable success in computer vision tasks such as image classification, segmentation, and super-resolution. However, these advances come at a high computational cost, typically requiring power-hungry GPUs and large-scale datasets for training. A significant contributor to this burden is the self-attention mechanism, particularly in transformer-based architectures, whose computational complexity grows quadratically with input size. While inductive biases—such as those embedded in convolutional neural networks (CNNs)—can mitigate data requirements by encoding spatial locality, they often lack the flexibility and long-range modeling capabilities offered by attention mechanisms.\\
Hybrid approaches that combine convolutions with more efficient forms of attention have been proposed to strike a balance between performance and resource usage. Nevertheless, these models still rely heavily on image unrolling and dense token interactions, leading to substantial memory and computation demands.

\subsection{Goals}
To address these challenges, we propose WaveMix, a novel neural architecture that replaces self-attention with an efficient frequency-domain alternative for spatial token mixing. At the core of WaveMix is the multi-level 2D Discrete Wavelet Transform (DWT), which enables hierarchical decomposition of input images without the need for unrolling. Unlike attention-based methods, DWT preserves the spatial resolution while reorganizing image information in a way that naturally encodes several powerful inductive priors: scale-invariance, shift-invariance, and sparsity of edges.

The DWT is a lossless transformation that maintains the overall information content (i.e., the total number of spatial tokens remains unchanged), while emphasizing high-frequency details that are crucial for image super-resolution. Importantly, it introduces no additional parameters and expands the receptive field more efficiently than stacked convolutional layers, allowing the model to capture both global context and fine-grained details with minimal overhead.

WaveMix thus provides an effective and lightweight alternative to traditional vision architectures, particularly in resource-constrained environments. By leveraging frequency-domain insights, it opens up new directions for designing scalable and interpretable models for high-resolution image reconstruction and other dense prediction tasks.